\Large{Learning to Pivot with Adversarial Networks}

### 2016-10-31 tex/paper.tex
save

The classification challenge used here is common in jet substructure
studies (see \citep{Khachatryan:2014vla,ATL-PHYS-PUB-2015-033,wbosonATLAS} and
references therein): we aim to discriminate between  the normal jets produced copiously
at the LHC ($y=0$) and  the fat jets coming from an exotic process ($y=1$).
We reuse the datasets used in reference
\citep{baldi2016jet}.  For completeness, the jets are built with the
anti-$k_T$ algorithm \citep{Cacciari:2008gp}
with radius parameter $R=1.2$, and trimmed \citep{Krohn:2009th} with subjets built with
the $k_T$ algorithm and parameter $f_{cut}=0.2$. The features used
in the classifiers are: trimmed jet invariant mass, N-subjettiness
$\tau_{21}^{\beta=1}$ \citep{nsub,Thaler2012}, and the energy correlation
functions \citep{Larkoski2013} $C_{2}^{\beta=1}$, $C_{2}^{\beta=2}$,
$D_{2}^{\beta=1}$, $D_{2}^{\beta=2}$.

>>>>

The classification challenge used here is common in jet substructure
studies (see \citep{Khachatryan:2014vla,ATL-PHYS-PUB-2015-033,wbosonATLAS} and
references therein): we aim to discriminate between  the normal jets produced copiously
at the LHC ($Y=0$) and  the fat jets coming from an exotic process ($Y=1$).
We reuse the datasets used in reference
\citep{baldi2016jet}.  For completeness, the jets are built with the
anti-$k_T$ algorithm \citep{Cacciari:2008gp}
with radius parameter $R=1.2$, and trimmed \citep{Krohn:2009th} with subjets built with
the $k_T$ algorithm and parameter $f_{cut}=0.2$. The features used
in the classifiers are: trimmed jet invariant mass, N-subjettiness
$\tau_{21}^{\beta=1}$ \citep{nsub,Thaler2012}, and the energy correlation
functions \citep{Larkoski2013} $C_{2}^{\beta=1}$, $C_{2}^{\beta=2}$,
$D_{2}^{\beta=1}$, $D_{2}^{\beta=2}$.
